Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2023-02-17 paper/paper.tex
Remove unused figures
Add corrections to intro

\section{Introduction} \label{sec:intro}
In recent years, aerospace stakeholders have realized that avionics systems are subject to possible cyber-attacks just like other cyber-physical systems.
%
\footnote{This work was funded in part by the
Defense Advanced Research Projects Agency (DARPA) CASE program.
%
The views expressed are those of the authors and do not reflect the official
policy or position of DARPA or the U.S. Government.}
%
Thus, in addition to being fault-tolerant, safety-critical avionics systems must also be {\em cyber-resilient}.
%
Cyber-resiliency means that the system is tolerant to cyber-attacks just as safety-criticalsystems are tolerant to random faults: they recover and continue to execute their mission function, or safely shut down, as requirements dictate.

Unfortunately, systems engineers are currently given few development tools to help answer even basic questions about potential vulnerabilities and ways to mitigate vulnerabilities.  They instead rely on process-oriented checklists and guidelines.
%
Cyber vulnerabilities are often discovered during penetration testing late in the development process;
%
or worse yet, they may be discovered only after the product has been fielded, necessitating extremely expensive and time-consuming remediation. This is not a sustainable development model.

We have been developing the {\em BriefCASE} \oldjunk{toolsuite} toolkit to address this need.
%
\brfcs\ is a Model-Based Systems Engineering (MBSE) environment built in the Open Source AADL Tool Environment (OSATE) to add new capabilities for building cyber-resilient systems.
%
\footnote{AADL is the acronym for Architecture Analysis and Design Language~\cite{aadl}.}
%
In this paper we describe how it facilitates specifying, testing, verifying, and synthesizing high assurance components inserted into a system to improve its cyber-resiliency.
%
The main organizing concept is that of an architecture-to-architecture \emph{security-improving transform}, achieved via the insertion of new architectural components aimed at mitigating cyber-vulnerabilities.
%
We describe two such transformations in this paper: (1) the insertion of a filter to prevent malformed data from a malicious actor being propagated to downstream components, and (2) the insertion of a runtime monitor to detect (and alert) unexpected behaviors arising from untrusted components.
%
We refer to these as \emph{high-assurance components} because they must be correct and fulfill their intended purpose for the system to be cyber-resilient.

@@

As indicated in the preceding discussion, {\brfcs} is aimed at addressing the lack of tool support for the problem of enforcing and implementing the class of cyber-resilience system requirements.
%
Our approach to the problem is embedded in a substantial collection of tools to be wholistic in addressing cyber-resilience at the system level, so it is important to clarify the
research impact.
%
We see the following as the distinguishing contributions of this paper:
\begin{compactitem}
  \item The language and semantics of \emph{code contracts} as a means to join system-level contract analysis results (arising from model checking) with component implementation correctness results (arising from property-preserving code generation).
  \item \emph{Test contracts} as a stylized mechanism to unit test code contracts inside the \brfcs\ framework with \agr.
  \item A strong formal path connecting (A) top-level system cyber-resilience requirements, (B) specifications for high-assurance components inserted to mitigate against specific cyber-resilience problems, and (C) synthesis to a programming language with a verified compiler.
  \item A case study that demonstrates the use of \brfcs\ to add cyber-resiliency to a non-trivial UAV system.
\end{compactitem}

Our approach currently applies to common cyber-vulnerabilities, such as buffer overflow, lack of input validation, and supply-chain issues;
%
however, other cyber-vulnerabilities such as side-channel attacks and denial of service have not yet been addressed. Moreover, this work does not introduce a new type of high-assurance component in terms of capability.
%
Instead, our contribution is in the automated synthesis of security-improving components from formal cyber-resilience specifications, paired with a verification showing that the synthesized implementation is correct in the context of the whole system all the way down to the binary implementation.

We have not yet tried to apply {\brfcs} to problems outside the realm of cyber-resilience;
%
however, the notions of code and test contracts, along with the system analysis and verified code generation facilities promise to be useful in a wide variety of settings.
%
Writing code and test contracts does require a working knowledge of propositional logic but not to a degree that would exceed what would be expected in a designer.
%
The general synthesis approach in this paper could be used outside of the \brfcs\ environment, but it would only then provide guarantees relative to the complied artifacts and not say anything about the correctness of the system composition.

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=2\columnwidth]{figs/sw-initial.png}
	\caption{Initial software architecture.}
	\label{fig:sw-initial}
\end{figure*}

>>>>

\section{Introduction} \label{sec:intro}
In recent years, aerospace stakeholders have realized that avionics systems are subject to possible cyber-attacks just like other cyber-physical systems.
%
\footnote{This work was funded in part by the
Defense Advanced Research Projects Agency (DARPA) CASE program.
%
The views expressed are those of the authors and do not reflect the official
policy or position of DARPA or the U.S. Government.}
%
Thus, in addition to being fault-tolerant, safety-critical avionics systems must also be {\em cyber-resilient}.
%
Cyber-resiliency means that the system is tolerant to cyber-attacks just as safety-critical systems are tolerant to random faults: they recover and continue to execute their mission function, or safely shut down, as requirements dictate.

Unfortunately, systems designers are currently given few development tools to help answer even basic questions about potential vulnerabilities and ways to mitigate vulnerabilities.
%
They instead rely on process-oriented checklists and guidelines.
%
Cyber vulnerabilities are often discovered during penetration testing late in the development process;
%
or worse yet, they may be discovered only after the product has been fielded, necessitating extremely expensive and time-consuming remediation. This is not a sustainable development model.

We have been developing the {\em BriefCASE} toolkit to address this need.
%
\brfcs\ is a Model-Based Systems Engineering (MBSE) environment that is integrated into the Open Source AADL Tool Environment (OSATE).
%
\footnote{AADL is the acronym for Architecture Analysis and Design Language~\cite{aadl}.}
%
It adds new capabilities for building cyber-resilient systems.
%
In this paper we describe how it facilitates specifying, testing, verifying, and synthesizing high assurance components inserted into a system to improve its cyber-resiliency.

The main organizing concept is that of an architecture-to-architecture \emph{security-improving transform}, achieved via the insertion of new architectural components aimed at mitigating cyber-vulnerabilities.
%
We describe two such transformations in this paper: (1) the insertion of a filter to prevent malformed data from a malicious actor being propagated to downstream components, and (2) the insertion of a runtime monitor to detect (and alert) unexpected behaviors arising from untrusted components.
%
We refer to these as \emph{high-assurance components} because they must be correct and fulfill their intended purpose for the system to be cyber-resilient.

@@

As indicated in the preceding discussion, {\brfcs} is aimed at addressing the lack of tool support for the problem of enforcing and implementing cyber-resilience system requirements.
%
Our approach to the problem is embedded in a collection of tools that together are intended to be wholistic in addressing cyber-resilience at the system level, so it is important to clarify the
research impact.
%
We see the following as the distinguishing contributions of this paper:
\begin{compactitem}
  \item The language and semantics of \emph{code contracts} as a means to join system-level contract analysis results (arising from model checking) with component implementation correctness results (arising from property-preserving code generation).
  \item \emph{Test contracts} as a stylized mechanism to unit test code contracts inside the \brfcs\ framework with \agr.
  \item A strong formal path connecting (A) top-level system cyber-resilience requirements, (B) specifications for high-assurance components inserted to mitigate against specific cyber-resilience problems, and (C) synthesis to a programming language with a verified compiler.
  \item A case study that demonstrates the use of \brfcs\ to add cyber-resiliency to a non-trivial UAV system.
\end{compactitem}

Our approach currently applies to common cyber-vulnerabilities, such as buffer overflow, lack of input validation, and supply-chain issues.
%
Other cyber-vulnerabilities such as side-channel attacks and denial of service have not yet been addressed. Moreover, this work does not introduce a new type of high-assurance component in terms of capability.
%
Instead, our contribution is in the automated synthesis of security-improving components from formal cyber-resilience specifications, paired with a verification showing that the synthesized implementation is correct in the context of the whole system all the way down to the binary implementation.

We have not yet tried to apply {\brfcs} to problems outside the realm of cyber-resilience;
%
however, the notions of code and test contracts, along with the system analysis and verified code generation facilities should be useful in a wide variety of settings.
%
Writing code and test contracts does require a working knowledge of propositional logic but not to a degree that would exceed what would be expected in a designer.
%
The general synthesis approach in this paper could be used outside of the \brfcs\ environment, but it would only then provide guarantees relative to the complied artifacts and not say anything about the correctness of the system composition.

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=2\columnwidth]{figs/sw-initial.PNG}
	\caption{Initial software architecture.}
	\label{fig:sw-initial}
\end{figure*}
